Hydra battles in Coq

### 2020-10-05 doc/hydras.tex
minor modifications

We prove in \coq{} the following results:

@@

Our definition may look more complex than the mathematical one, but
uses plain structural recursion over the type \coqsimple{T1}. Thus, tactics like
\coqsimple{cbn}, \coqsimple{simpl}, \coqsimple{compute}, etc., are applicable. For simplicity's sake, 
we used an auxiliary function \texttt{canonS} of type \texttt{T1 -> nat  -> T1} such that
(\texttt{canonS  $\alpha$ $i$}) is equal to $\canonseq{\alpha}{i+1}$.

@@

The following function computes $\canonseq{\alpha}{i}$, except for the case $i=0$, where it simply returns $0$\;\footnote{This restriction did not prevent us from proving all the main theorems of~\cite{KS81, KP82}. Nevertheless, in a future version of this development, we may define $\canonseq{\alpha}{0}$ exactly as 
in~\cite{KS81}. This would  be done at the cost of making proofs much more complex.}.

@@

Proving the equality $\canonseq{\alpha+1}{i}=\alpha$ is not 
as simple as suggested by the equations of definition~\ref{def:canonseq-math}\,.
Nevertheless, we could prove it by  structural induction on $\alpha$.

@@

First, we prove by transfinite induction over $\alpha$ that $\canonseq{\alpha}{i+1}$ is an ordinal strictly less than $\alpha$ (assuming $\alpha\not=0$). This property allows us to use the function \texttt{canonS} and its derivates in function definitions by transfinite recursion.

@@

Note the use of \coq's \texttt{sig} type in the theorem's statement, which
relates the boolean function \texttt{is\_limit} defined on the \texttt{T1} data-type with a constructive view of the limit of a sequence: for any $\beta<\lambda$, we can compute an item of the canonical sequence of $\lambda$ which is greater than $\beta$.

>>>>

We prove in \coq{} the following result:

@@

Our definition may look more complex than the mathematical one, but
uses plain structural recursion over the type \coqsimple{T1}. Thus, tactics like
\coqsimple{cbn}, \coqsimple{simpl}, \coqsimple{compute}, etc., are applicable. For simplicity's sake, 
we use an auxiliary function \texttt{canonS} of type \texttt{T1 -> nat  -> T1} such that
(\texttt{canonS  $\alpha$ $i$}) is equal to $\canonseq{\alpha}{i+1}$.

@@

The following function computes $\canonseq{\alpha}{i}$, except for the case $i=0$, where it simply returns $0$\;\footnote{This restriction did not prevent us from proving all the main theorems of~\cite{KS81, KP82}. Nevertheless, in a future version of this development, we may define $\canonseq{\alpha}{0}$ exactly as 
in~\cite{KS81}. But we are afraid this would  be done at the cost of making some proofs much more complex.}.

@@

Proving the equality $\canonseq{\alpha+1}{i}=\alpha$ is not 
as simple as suggested by the equations of definition~\ref{def:canonseq-math}\,.
Nevertheless, we can prove it by  plain structural induction on $\alpha$.

@@

We prove by transfinite induction over $\alpha$ that $\canonseq{\alpha}{i+1}$ is an ordinal strictly less than $\alpha$ (assuming $\alpha\not=0$). This property allows us to use the function \texttt{canonS} and its derivates in function definitions by transfinite recursion.

@@

Note the use of \coq's \texttt{sig} type in the theorem's statement, which
relates the boolean function \texttt{limitb} defined on the \texttt{T1} data-type with a constructive view of the limit of a sequence: for any $\beta<\lambda$, we can compute an item of the canonical sequence of $\lambda$ which is greater than $\beta$.
